Baseline centering problem

### 2018-11-25 paper/tangotd.tex

The Dirichlet norm associated with $\rho$ is $\E_{ss'}
(f(s)-f(s'))^2$. Its matrix is $\rho+\rho'-\rho P-\transp{(\rho P)}$ where
$\rho'$ is the distribution of $s'$.
A local minimizer of the Dirichlet error between $V$ and
$(\Id-P)^{-1}R$ solves
\begin{equation}
\transp{\Phi} (\rho+\rho'-\rho P-\transp{(\rho P)})(V-(\Id-P)^{-1}R)=0
\end{equation}
If $\rho$ is the stationary distribution $\mu$ and $P$ is reversible, one
has $\transp{(\mu P)}=\mu P$ so $\rho+\rho'-\rho P-\transp{(\rho
P)}=2\mu(\Id-P)$ and this is equivalent to
\begin{equation}
\transp{\Phi}\mu ((\Id-P)V-R)=0
\end{equation}
namely, the same as a fixed point of TD.

@@

TD is the only one of those fixed point equations that is
\emph{samplable} given that we can sample $\rho$, $\rho P$ and $\rho R$.
\footnote{Actually the minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is also samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, the $\rho^2$ is a bit weird... but some of the algos we consider
below actually amount to this.
}
Thus, from now on we are going to focus on solving
\begin{equation}
\transp{\Phi}\rho (\Id-P)V=\transp{\Phi}\rho R
\end{equation}
using various SGD-like solvers.

@@

One-and-a-half-timescale needs more independence than two-timescale. I
\emph{think} that two-timescale can deal with taking the same sample for
$A$ and $\transp{A}$ in $\transp{A}(...)^{-1}A$, and taking correlated
consecutive samples (eg, online) for the matrix to be inverted. I think
TANGO would need uncorrelated samples for the matrix to be inverted (eg,
a replay buffer) and two samples for $A$ and $\transp{A}$, but not sure
about the latter.

>>>>

The Dirichlet norm associated with $\rho$ is $\E_{ss'}
(f(s)-f(s'))^2$. Its matrix is $\rho+\rho'-\rho P-\transp{(\rho P)}$ where
$\rho'$ is the distribution of $s'$.
A local minimizer of the Dirichlet error between $V$ and
$(\Id-P)^{-1}R$ solves
\begin{equation}
\transp{\Phi} (\rho+\rho'-\rho P-\transp{(\rho P)})(V-(\Id-P)^{-1}R)=0
\end{equation}
If $\rho$ is the stationary distribution $\mu$ and $P$ is reversible, one
has $\transp{(\mu P)}=\mu P$ and $\rho'=\mu$ so $\rho+\rho'-\rho P-\transp{(\rho
P)}=2\mu(\Id-P)$ and this is equivalent to
\begin{equation}
\transp{\Phi}\mu ((\Id-P)V-R)=0
\end{equation}
namely, the same as a fixed point of TD.

@@

TD is the only one of those fixed point equations that is
\emph{samplable} given that we can sample $\rho$, $\rho P$ and $\rho R$.
\footnote{Actually the minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is also samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, the $\rho^2$ is a bit weird... moreover having
$\transp{\Delta}\Delta$ means we are just facing the double sampling
problem.
}
Thus, from now on we are going to focus on solving
\begin{equation}
\transp{\Phi}\rho (\Id-P)V=\transp{\Phi}\rho R
\end{equation}
using various SGD-like solvers.

@@

Almost-one-timescale (such as TANGO) needs more independence than two-timescale. I
\emph{think} that two-timescale can deal with taking the same sample for
$A$ and $\transp{A}$ in $\transp{A}(...)^{-1}A$, and taking correlated
consecutive samples (eg, online) for the matrix to be inverted. I think
TANGO would need uncorrelated samples for the matrix to be inverted (eg,
a replay buffer) and two samples for $A$ and $\transp{A}$, but not sure
about the latter.
